Introduction

### 2021-10-05 Manuscript/Manuscript_Introduction.Rmd
small edits and added references

The article collection and screening phases of a systematic review are particularly problematic tasks [systematic review tutorial]. First, relevant published research needs to be collected from scientific databases through appropriately built search queries. The construction of search queries is a particularly delicate task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages; the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching]. If an integrated search tool is not used, manual work is required to download, store and organize the publication data. Searching manually may be complicated by limits in the number of records that can be downloaded at once [] and the necessity to harmonize different formats and resolve duplication. The citation screening phase consists of classifying the collected publications as relevant or not for the topic of interest [@bannach2019machine]. It is usually the more resource-demanding task of a systematic review: even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching]. It was estimated that labelling 10 000 publications may take as much as 40 weeks of work, while the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating]. A consequence is that often systematic reviews are already outdated once they are published [@beller2013systematic].\

@@

We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains. The systematic review protocol is published in [].

>>>>

The article collection and screening phases of a systematic review are particularly problematic tasks [@babar2009systematic]. First, relevant published research needs to be collected from scientific databases through appropriately built search queries (retrieval phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane]. The construction of search queries is a particularly delicate task [@lefebvre2011searching; @hammerstrom2010searching], requiring both domain and some knowledge of the databases' query languages; the goal is to produce a set of results containing all relevant articles (high sensitivity) while keeping the total number low (high specificity), focusing on the first aspect at the cost of the second [@hammerstrom2010searching]. If an integrated search tool is not used, manual work is required to download, store and organize the publication data. Searching manually may be complicated by limits in the number of records that can be downloaded at once [] and the necessity to harmonize different formats and resolve duplication. The citation screening phase consists of classifying the collected publications as relevant or not for the topic of interest (appraisal phase) [@bannach2019machine; @tsafnat2014systematic; @higgins2019cochrane]. It is usually the more resource-demanding task of a systematic review: even with appropriately built search queries, the returned results easily range in the tens of thousands of which just a small fraction is actually relevant [@lefebvre2011searching]. It was estimated that labelling 10 000 publications may take as much as 40 weeks of work, while the average clinical systematic review takes 63 weeks to be completed [@bannach2019machine; @borah2017analysis; @allen1999estimating]. A consequence is that often systematic reviews are already outdated once they are published [@beller2013systematic].\

@@

We apply this solution in the production of a systematic review evaluating the mathematical modelling of patient referral networks among hospitals and their impact on the diffusion of healthcare-associated pathogenic microorganisms with a focus on antimicrobial-resistant strains. The systematic review protocol is published in [@newis].
